Further Evidence of Modified Spin-down in Sun-like Stars:\\Pile-ups in the Temperature--Period Distribution

### 2022-02-03 src/ms.tex
JVS comments

After a period of slowed spin-evolution, stars must resume spinning down as evidenced from studies of older open clusters. From open cluster data \citet{Curtis2020} estimated that solar-mass stars resume spin-down after an age of $\approx$~230~Myr. Thus, if core–envelope coupling is responsible for delaying the spin-down of stars, and if the theoretical core–envelope coupling timescales are accurate, then we may expect Sun-like stars to experience little spin evolution between $\sim$100~Myr and $\sim$200~Myr. This picture is compatible with open cluster studies which show multiple cluster sequences of Sun-like stars overlapping at ages of $\sim$100--200~Myr, with spin-down resuming by $\sim$200--300~Myr \citep{Fritzewski2020,Fritzewski2021}.

%JVS: I am not sure this is actually what you expect to see. If you go back and look at the Lanzafame and Spada paper from 2015, the spin down never stalls out entirely... there is always evolution in the period, even though it is slower than you would have predicted with a solid body model. In the solar mass stars, you never see something as stark as the Praesepe/NGC6811 overlap. You're also working in a regime where initial conditions, saturated spin down, and cluster age uncertainties can really get you. I'm not sure you can attribute the overlap in Fritzewski to core-envelope decoupling... it could also just be you are looking at clusters that are coeval within the age uncertainties (remember, you're dealing with isochrone ages that come from stars with convective cores at these ages, and they have *nasty* systematic shifts depending on what you assumed about the degree of convective core overshooting).  I would tread carefully here.

>>>>

After a period of slowed spin-evolution, stars must resume spinning down as evidenced from studies of older open clusters. From open cluster data \citet{Curtis2020} estimated that solar-mass stars resume spin-down after an age of $\approx$~230~Myr. Thus, if core–envelope coupling is responsible for delaying the spin-down of stars, and if the theoretical core–envelope coupling timescales are accurate, then we may expect Sun-like stars to experience slowed spin evolution between $\sim$100~Myr and $\sim$200~Myr. This picture is compatible with open cluster studies which show multiple cluster sequences of Sun-like stars overlapping at ages of $\sim$100--200~Myr, with spin-down resuming by $\sim$200--300~Myr \citep{Fritzewski2020,Fritzewski2021}. However, an alternative explanation for the overlapping cluster sequences observed by those authors could be that the clusters are in fact coeval.
